---
title: "Assigment - kNN DIY"
author:
  - Jorian Roelofs - Author
  - Rick Messing - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---
##This is the version with the mistakes!!!!!!!!!!!!!!!!!!!!!!!!!!!!

```{r}
library(tidyverse)
library(googlesheets4)
library(caret)
```

---

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train  your own kNN model. Follow all the steps from the CRISP-DM model.




## Business Understanding
text and code here

## Data Understanding
text and code here

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)
```
```{r}
str(rawDF)
```


## Data Preparation
At first i want to clean the data so that i will only use the relevant information. 
So what i am doing next is removing de date's in the rawDF file since it will not be used

```{r}
##randomize
cleanDF_R <- rawDF[sample(1:nrow(rawDF)),]
cleanDF <- cleanDF_R
head(cleanDF)
```
At the variable Occupancy contains of two different outcomes, namely 1 or 0. This likely indicates
the "occupancy" for either true or false

So now i will be counting each of these outcomes and the percentage it occurs

```{r}
cntOcc <- table(cleanDF$Occupancy)
propOcc <- round(prop.table(cntOcc)*100, digits = 1)

cntOcc
propOcc
```

Now i am going to change the variable type from character to facter using the function "factor",
it will now saw "Occupancy" or "No occupancy"

```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("0", "1"), labels = c("No occupancy", "Occupancy")) %>% relevel("Occupancy")
head(cleanDF)
```
Now i am going to look at some different measurements using "summery"

```{r}
summary(cleanDF[c("Temperature", "Humidity", "Light", "CO2")])
```

Here i apply normalization to rescale all the features to a standard range of values

```{r}
normalize <- function(x) { 
  return ((x - min(x)) / (max(x) - min(x))) 
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")
cat("Normalized testSet1:", normalize(testSet1), "\n")
cat("Normalized testSet2:", normalize(testSet2))

```

The next code puts "Occupancy" at the front of the table
```{r}
cleanDF <- cleanDF[, c(1,2,6,4,5,3)]
head(cleanDF)
```
Applying the normalize function to each feature using the sapply function
```{r}
cleanDF_n <- sapply(2:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n[,1:5])
```

Testing the normalization

```{r}
trainDF_feat <- cleanDF_n[1:7000,  ]
testDF_feat <- cleanDF_n[7001:8143,  ]

trainDF_labels <- cleanDF[1:7000,  1]
testDF_labels <- cleanDF[7001:8143,  1]
```

## Modeling

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 21)
head(cleanDF_test_pred)
```

```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

## Evaluation and Deployment
text and code here

reviewer adds suggestions for improving the model
